Dark matter halo shapes at $z=0$ in the Auriga simulations

### 2019-07-19 Document/paper.tex
replace

% Abstract of the paper
\begin{abstract}
We present shape measurements of Milky Way sized dark matter halos at
redshift $z=0$ in a suite of 30 zoom simulations from the Auriga
project. 
We compare the results in full magnetohydrodynamics against dark
matter only physics. 
We find a strong influence of baryons in making dark matter halos
rounder at all radii compared to its dark matter only counterparts.
At distances $\lesssim 30$ kpc, rounder and coherent dark matter
distributions correlate with extended massive stellar disks and low gas
densities.  
We measure the alignment between the halo and the stellar disk and
find almost perfect alignment at $0.25R_{200}\sim56$ kpc.   
In some cases the alignment between the two components significantly
changes as a function of radius implying that the halo shape twists;
this effect correlates with extended stellar disks and
low gas densities and is almost absent in the dark matter only
simulations.  
In a comparison against observational constraints  we find that $20\%$
of halos are consistent with observational results derived
from the Pal 5 stream that favor an almost spherical shape.
Including baryons is a required element to achieve this
level of agreement. In contrast, none of the simulations (dark matter
only nor with baryons) match the constrains derived from the
Sagittarius stream favoring an oblate dark matter halo.
\end{abstract}

@@

Our physical picture of the Universe as a whole has be shaped by
accurate observations and modeling of our own Galaxy. 
Explaining the matter budget and kinematical state of the Milky Way
(MW) is  equivalent to figuring out its formation process in a
cosmological context. 
As a first approximation, the MW morphology and
separation into global kinematically coherent components, such as its
disk and bulge, can be used to support the  existence of a Dark Matter
(DM) component to explain its dynamics around the solar neighborhood
\citep{2000MNRAS.311..361O,2009PASJ...61..227S,2010JCAP...08..004C,2013ApJ...779..115B,Iocco15}.

@@

These two questions have been difficult to address because for a long
time it was difficult to produce realistic galactic disks within the
CDM context.
The success of such enterprise has been the result of high numerical
resolution and the understanding that baryonic effects such as stellar
feedback and black hole feedback play an important role in forming a
galactic disk resembling the Milky Way.
Along the way numerical experiments show that the baryonic effects also impact
the dark matter halo shape making the halo rounder than it otherwise
be in a dark matter only simulation
\citep{Dubinski94,Debattista08,Kazantzidis10,Abadi10,Bryan13,Chua19,Artale19}. 
High resolution simulations have also allowed detailed studies of the
alignment between the stellar disk and the dark matter halo
\citep{Bailin05,DeBuhr12,Debattista13,Gomez17}.

@@

In this paper we contribute to the debate by reporting measurements of
the DM halo shape in MW type galaxies from state-of-the-art simulations from the
Auriga project.
These simulations have large enough numerical resolution, and explicit
cosmological context and an appropriate feedback physics to produce
realistic MW disks.
This paper is structured as follows. 
In Section \ref{sec:numerical} we present the most relevant details of
the simulations, in Section \ref{sec:method} we present the method
that we use to measure the DM halo shape. 
In Section \ref{sec:results} we present our results focusing on the
radial shape trends at $z=0$ and the alignments with the stellar disk.
We discuss our results in Section \ref{sec:discussion} to place them
into the context of other numerical work, explore correlations of the
shape with baryonic properties in the disk and finally make a direct
comparison against observational constraints for the MW's dark matter halo shape.
We finalize with our conclusions in Section \ref{sec:conclusions}.

@@

The Auriga project offers cosmological zoom in simulations of MW-sized 
dark matter halos in a $\Lambda$CDM cosmology. 
This simulations come in two versions: dark matter only (DMO) and
baryonic physics including magetohydrodynamics (MHD).
A detailed description of the simulations and their disk properties
can be founc in \citep{auriga}, here we summarize its main features.

@@

\begin{figure*}
\subfloat[DMO simulations.]{\includegraphics[width=0.8\columnwidth]{triaxialiy_distro_DM.pdf}}
\subfloat[MHD simulations.]{\includegraphics[width=0.8\columnwidth]{triaxialiy_distro_MHD.pdf}}
\caption{Cumulative distribution for the triaxiality at five different radii.
  Right/left panel correspond to DMO/MHD simulations, respectively. 
  In DMO simulations the median triaxiality at all radii is larger
  than $0.5$; only for $20\%$ the triaxility is smaller than $0.5$.
  Furthermore, the triaxility increases as one moves towards the inner
  part of the halo.
  In MHD simulations the situation is reversed.
  The median triaxility at all radii is smaller than $0.5$.
  Moving towards the stellar disk the triaxility decreases towards a median
  value of $T=0.15$.}
\label{fig:triaxial_cumulative}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{angles_alignment_DM.pdf}
\includegraphics[width=1.0\textwidth]{angles_alignment_MHD.pdf}
\end{center}
\caption{Angles between the
  principal axis of the halo shape and the principal axis of the
  stellar disk in the MHD simulations at four different radii $\leq 0.5R_{200}$.
  Thin lines correspond to each one of the thirty halos in our sample,
  while the thick line traces the median value.
  Each panel compares the alignment of the corresponding
  major/middle/minor axis both in the halo and the stellar disk.
  In the upper row the haloes come from the DMO simulation, 
  showing that the ellipsoids describing the
  shape are constant as a function of radius for the most part of the
  sample.
  In the lower row the haloes come from the MHD simulation providing a 
  self-consistent comparison with the stellar disks. 
  In this case the dark matter shells twist in all the halos.
  The degree of this twisting is different in each halo.
  Interestingly, an almost perfect halo-disk alignment happens across
  the sample at an intermediate radius of $0.25R_{200}$ ($56\pm 4$kpc).
}
\label{fig:cumulative_alignment}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{correlations_twisting_triaxiality_MHD.pdf}
\end{center}
\caption{Changse of angle alignment of the dark
  matter halo and stellar disk at two different radii ($R_{200}/16$
  and $0.25R_{200}$) as a function of the baryonic disk properties
  already explored in Figure \ref{fig:disk_correlations}.  
  Figure \ref{fig:cumulative_alignment} showed that maximum alignment
  occurs at $0.25R_{200}$ while in the inner regions ($R_{200}/16$)
  considerable missalignments occurr.
 at different radii
 and baryonic disk properties. 
 The label with the $\rho$ value corresponds to the Spearman’s rank correlation coefficient. }
\label{fig:alignment_correlations}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\textwidth]{correlation_T_MHD_disk.pdf}
\end{center}
\caption{Correlations between the halo triaxility at different radii
  and baryonic disk properties. 
  The label with the $\rho$ value corresponds to the Spearman's rank
  correlation coefficient.
  The line is the best linear minimum squares fit.
  The x-axis in the first column is the gas density at the center of
  the galaxy with in a sphere of radius  $1$ kpc \citep{Pakmor17};
  the second column shows the disk to total mass ratio and the last
  column includes the disk optical radius defined to be the radius at which the
  $B$-band surface brightness drops below 25 mag arcsec$^{-2}$ \citep{auriga}.
  The largest correlations are found for the two smaller radii and
  dilute as one approached $R_{200}$.
  Large and massive stellar disks with a low gas content are
  correlated with low dark matter triaxilities.}
\label{fig:disk_correlations}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{correlations_angles_alignment_MHD.pdf}
\end{center}
\caption{Changse of angle alignment of the dark
  matter halo and stellar disk at two different radii ($R_{200}/16$
  and $0.25R_{200}$) as a function of the baryonic disk properties
  already explored in Figure \ref{fig:disk_correlations}.  
  Figure \ref{fig:cumulative_alignment} showed that maximum alignment
  occurs at $0.25R_{200}$ while in the inner regions ($R_{200}/16$)
  considerable missalignments occurr.
 at different radii
 and baryonic disk properties. 
 The label with the $\rho$ value corresponds to the Spearman’s rank correlation coefficient. }
\label{fig:alignment_correlations}
\end{figure*}

@@

The left panel of this Figure shows that in the DMO sample the
triaxility has a median larger than $0.5$ at all radii, furthermore
this median value increases as we move towards the inner part of the
halo.
The right panel shows the exact complementary picture in the MHD
sampe.
There the median triaxility is alwas smaller than $0.5$ and this
triaxility is smaller as we move closer to the galactic disk.

@@

\subsection{Alignments with the stellar disk}

A common assumption in observational models of the MW DM halo is that
its minor axis is perfectly aligned with the stellar disk minor axis.
Although it is a reasonable assumption to guarantee the stability of
the galactic disk in simplified models of isolated galaxies, this
might not hold in an explicit cosmological context. 
To examine the degree of validity of this assumption we study in this
section the alignment between the eigenvectors of the inertia tensor of
stellar particles within $0.1R_{200}$ ($\sim 23\pm 2$ kpc) and the
eigenvectors of the dark matter halo shape.
All the measurements are done at $z=0$.

In Figure \ref{fig:cumulative_alignment} we summarize our main results
regarding these alignments with the halo shape measured at five
different radii.
The upper row shows the alignment of the halos in the DMO simulations
with the stellar disk in the MHD simulations.
The main objective of this measurement is to calibrate the radial
evolution of the DM halo shape. 
We find that the DM shape remains constant with radius.

The lower row in Figure \ref{fig:cumulative_alignment} shows the
alignments with the halo in the MHD simulations. 
This time the halo shape changes and twists at different radii.
However around the radius of $0.25R_{200}$ there is an alignment
almost perfect between the shapes of the stellar disk and the dark
matter halo. 
Above and below this radius there are halos with a lower degree of
alignment.
Across the three different alignments we measure we verify that the
strongest one is indeed the one between the two minor axis.

@@

The strength of the change depends on the numerical resolution, the
method to resolve the hydrodynamics and the models describing star
formation and stellar feedback \citep{Debattista08, Bryan13, Butsky16,
  Chua19, Artale19}.  
The key concept unifying these results is that the baryon distribution
influences and correlates with the dark matter halo shape. 
Here we find that the broad tendency is that massive stellar disks
correlate with spherical dark matter distributions.

In order to explore this idea in the Auriga simulations we quantify
the correlation between halo shape with baryonic disk properties. 
Looking into the measurements already reported by \cite{auriga} and
\cite{Pakmor17} we find three baryonic quantities that have the
strongest correlation with DM halo triaxiality: the central gas
density in a sphere of radius $1$kpc, the disk to total mass ratio and
the optical radius.

Figure \ref{fig:disk_correlations} shows the correlations of
these quantities with the triaxility at five diferent radii.
We use the Spearmen's rank correlation coefficient to quantify the
correlation strength.
We find that the strongest correlations are found with the halo shape
measured at radii smaller than $0.12R_{200}\sim 28$kpc, which 
is close to the upper limit of the disk optical radius among our
simulation sample. 
The trend is such that halos with large triaxiality correlate with
high gas density and stellar disks with low mass and small size.
In turn, massive and large stellar disks within a low density gas
environment correlate with low halo triaxiliaty.

Our second results deals with the disk-halo shape alignment as a function of
radius. 
In concordance with previous results in DM only simulations we find
that the shells of halo shape are well aligned at different radii.
However, in the presences of baryons these shells twist as a function
of radius.
At a radius of $0.25R_{200}\approx 56$ kpc the alignment between the
stellar disk and the dark matter halo is almost perfect and degrades
at other radii. 
This twisting effect, the change of disk-halo alignment as
a function of radius, is robust across our sample of 30
halos at all radii.
However, its strenght is not the same for all galaxies and strongly
correlates with halo triaxiality measured at $0.12R_{200}$.

\cite{Bailin05} studied the disk halo alignmnent as a function of
radius.
\cite{Gomez17} studied this in Auriga.
\cite{Debattista13} reported a similar twisting effect, but only at radii smaller
than the disk radius. 
At radii larger than the disk radius, they find, the dark matter
shells stop twisting. 
\cite{JingSuto02} also reported shell alignment twisting in their dark
matter only simulations as measured in the direction changes of large
and medium shape axis. 
They only had three high resolution MW-like halos (with
$\sim 10^{6}$ inside the virial radius) and could not make a
statistical statement about the impact of this effect.
However, they the twisting as an artifact resulting from high values of the
$c/b$ ratios that make the determination of the medium axis boisy.
Could then high triaxility values explain the twisting as a result of
erratic axis directions? 
If the triaxiality were the main culprit behind the twisting, the
correlation between the two quantities should be constant at every
radii.
In Figure \ref{fig:alignment_correlations} we already showed that this
correlation strongly depends on radius, we conclude that high
triaxiality values cannot be the full explanation.
Furthermore the twisting happens in such a way that it allows an
almost perfect alignment between the stellar disk at $0.1R{200}$ and
the halo shape measured at $0.25R_{200}$

We now use the results reported by \cite{LM10} and \cite{Bovy16}
to place our results in an observational context.
\cite{LM10} used observations of the Sagittarius tidal stream to
constrain the shape of the gravitational potential.
Their point of depart is that previous studies that assumed an
axisymetric galactic potential were not able to fit all the available
dynamic constraints for the Sagittarius stream, therefore making
necessary the use of a rigid triaxial potential with coaxial potential
ellipsoids for the dark matter component.  
Their results constrain the triaxility of this potential
component. 
They also translate ther results into a triaxiality of the density
contours (that could be compared against our results)
 to be $(c/a)=0.44$ and $(b/a)=0.97$ at a radius of $\sim 40$kpc. 
They do not report any uncertainties for these two values. 
Looking at their plots for the quality of fit criterion as a function
of dark halo axial scales (their Figure 5), we choose a conservative $10\%$
relative uncertainty.
One surprising element in their results is that  the major axis of the
halo shape is perpendicular to the stellar disk plane.

@@

In this paper we measured the shape of 30 isolated Milky Way like 
dark matter haloes simulated in the Auriga project using the zoom-in
technique. 
The Auriga project simulated these halos with two different setups:
dark matter only (DMO) simulation and full magnetohydrodynamics (MHD)
including star formation and feedback.
We used the shape measurement algorithm by \cite{Allgood06} on the
dark matter halos of these two kinds of simulations to quantify the
halo shape as a function of radius and the degree of aligment between
the stellar disk and the halo.

We find that MHD halos are rounder than DMO halos every sampled radii. 
MHD halos tend towards more oblate shapes ($T< 1/3$) DMO halos
tend towards more prolate shapes ($T>2/3$).  
The rounding effect is more noticeable as one moves closer to galactic
disk and strongly  correlates with baryonic properties of the disk
$\leq 0.10R_{200}\approx 20$kpc. 
More precisely, the triaxility is smaller for large and massive
stellar disks with low gas densities in its core $\leq 1$ kpc.

We also found that the alignment betwen the stellar disk and dark
matter halo changes with the radius.
At a radius of $0.25R_{200}$ the alignment is almost perfect and
degrades at smaller and larger distances.
This alignment evolution implies a radial twisting between the ellipsoids
describing the halo shape. 
We quantify this twist with the standard deviation of the angle
between the two minor axis at radii below $\leq 0.5R_{200}$ and find
that it strongly correlates is with the disk size and the core gas
mass density, there is only a weak correlation with the stellar mass
in the disk.

@@

From the purely numerical point of view a better understading of the
disk-halo alignment details will certainly require to study how the
halo and the disk co-evolved as a function of time.
Calibrating the effect of the cosmic web (both dark matter and gaseous)
\citep{2014MNRAS.443.1090F,2017MNRAS.469..594B,2019MNRAS.487.1607G}
could also be required to gain a full picture of this behaviour.

>>>>

% Abstract of the paper
\begin{abstract}
We present shape measurements of Milky Way sized dark matter halos at
redshift $z=0$ in a suite of 30 zoom simulations from the Auriga
project. 
We compare the results in full magnetohydrodynamics against dark
matter only physics. 
We find a strong influence of baryons in making dark matter halos
rounder at all radii compared to its dark matter only counterparts.
At distances $\lesssim 30$ kpc, rounder dark matter distributions
correlate with extended massive stellar discs and low gas 
densities.  
We measure the alignment between the halo and the stellar disc and
find almost perfect alignment at $0.25R_{200}\sim56$ kpc.   
In some cases the alignment between the two components significantly
changes as a function of radius implying that the halo shape twists;
this effect correlates with extended stellar discs and
low gas densities and is almost absent in the dark matter only
simulations.  
In a comparison against observational constraints  we find that $20\%$
of halos are consistent with observational results derived
from the Pal 5 stream that favor an almost spherical shape.
Including baryons is a required element to achieve this
level of agreement. In contrast, none of the simulations (dark matter
only nor with baryons) match the constrains derived from the
Sagittarius stream favoring an oblate dark matter halo.
\end{abstract}

@@

Our physical picture of the Universe as a whole has be shaped by
accurate observations and modeling of our own Galaxy. 
Explaining the matter budget and kinematical state of the Milky Way
(MW) is  equivalent to figuring out its formation process in a
cosmological context. 
As a first approximation, the MW morphology and
separation into global kinematically coherent components, such as its
disc and bulge, can be used to support the  existence of a Dark Matter
(DM) component to explain its dynamics around the solar neighborhood
\citep{2000MNRAS.311..361O,2009PASJ...61..227S,2010JCAP...08..004C,2013ApJ...779..115B,Iocco15}.

@@

These two questions have been difficult to address because for a long
time it was difficult to produce realistic galactic discs within the
CDM context.
The success of such enterprise has been the result of high numerical
resolution and the understanding that baryonic effects such as stellar
feedback and black hole feedback play an important role in forming a
galactic disc resembling the Milky Way.
Along the way numerical experiments show that the baryonic effects also impact
the dark matter halo shape making the halo rounder than it otherwise
be in a dark matter only simulation
\citep{Dubinski94,Debattista08,Kazantzidis10,Abadi10,Bryan13,Chua19,Artale19}. 
High resolution simulations have also allowed detailed studies of the
alignment between the stellar disc and the dark matter halo
\citep{Bailin05,DeBuhr12,Debattista13,Gomez17}.

@@

In this paper we contribute to the debate by reporting measurements of
the DM halo shape in MW type galaxies from state-of-the-art simulations from the
Auriga project.
These simulations have large enough numerical resolution, and explicit
cosmological context and an appropriate feedback physics to produce
realistic MW discs.
This paper is structured as follows. 
In Section \ref{sec:numerical} we present the most relevant details of
the simulations, in Section \ref{sec:method} we present the method
that we use to measure the DM halo shape. 
In Section \ref{sec:results} we present our results focusing on the
radial shape trends at $z=0$ and the alignments with the stellar disc.
We discuss our results in Section \ref{sec:discussion} to place them
into the context of other numerical work, explore correlations of the
shape with baryonic properties in the disc and finally make a direct
comparison against observational constraints for the MW's dark matter halo shape.
We finalize with our conclusions in Section \ref{sec:conclusions}.

@@

The Auriga project offers cosmological zoom in simulations of MW-sized 
dark matter halos in a $\Lambda$CDM cosmology. 
This simulations come in two versions: dark matter only (DMO) and
baryonic physics including magetohydrodynamics (MHD).
A detailed description of the simulations and their disc properties
can be founc in \citep{auriga}, here we summarize its main features.

@@

\begin{figure*}
\subfloat[DMO simulations.]{\includegraphics[width=0.8\columnwidth]{triaxialiy_distro_DM.pdf}}
\subfloat[MHD simulations.]{\includegraphics[width=0.8\columnwidth]{triaxialiy_distro_MHD.pdf}}
\caption{Cumulative distribution for the triaxiality at five different radii.
  Right/left panel correspond to DMO/MHD simulations, respectively. 
  In DMO simulations the median triaxiality at all radii is larger
  than $0.5$; only for $20\%$ the triaxility is smaller than $0.5$.
  Furthermore, the triaxility increases as one moves towards the inner
  part of the halo.
  In MHD simulations the situation is reversed.
  The median triaxility at all radii is smaller than $0.5$.
  Moving towards the stellar disc the triaxility decreases towards a median
  value of $T=0.15$.}
\label{fig:triaxial_cumulative}
\end{figure*}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{angles_alignment_DM.pdf}
\includegraphics[width=1.0\textwidth]{angles_alignment_MHD.pdf}
\end{center}
\caption{Angles between the
  principal axis of the halo shape and the principal axis of the
  stellar disc in the MHD simulations at four different radii $\leq 0.5R_{200}$.
  Thin lines correspond to each one of the thirty halos in our sample,
  while the thick line traces the median value.
  Each panel compares the alignment of the corresponding
  major/middle/minor axis both in the halo and the stellar disc.
  In the upper row the haloes come from the DMO simulation, 
  showing that the ellipsoids describing the
  shape are constant as a function of radius for the most part of the
  sample.
  In the lower row the haloes come from the MHD simulation providing a 
  self-consistent comparison with the stellar discs. 
  In this case the dark matter shells twist in all the halos.
  The degree of this twisting is different in each halo.
  Interestingly, an almost perfect halo-disc alignment happens across
  the sample at an intermediate radius of $0.25R_{200}$ ($56\pm 4$kpc).
}
\label{fig:cumulative_alignment}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=1.0\textwidth]{correlations_twisting_triaxiality_MHD.pdf}
\end{center}
\caption{Changse of angle alignment of the dark
  matter halo and stellar disc at two different radii ($R_{200}/16$
  and $0.25R_{200}$) as a function of the baryonic disc properties
  already explored in Figure \ref{fig:disc_correlations}.  
  Figure \ref{fig:cumulative_alignment} showed that maximum alignment
  occurs at $0.25R_{200}$ while in the inner regions ($R_{200}/16$)
  considerable missalignments occurr.
 at different radii
 and baryonic disc properties. 
 The label with the $\rho$ value corresponds to the Spearman’s rank correlation coefficient. }
\label{fig:alignment_correlations}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.8\textwidth]{correlation_T_MHD_disc.pdf}
\end{center}
\caption{Correlations between the halo triaxility at different radii
  and baryonic disc properties. 
  The label with the $\rho$ value corresponds to the Spearman's rank
  correlation coefficient.
  The line is the best linear minimum squares fit.
  The x-axis in the first column is the gas density at the center of
  the galaxy with in a sphere of radius  $1$ kpc \citep{Pakmor17};
  the second column shows the disc to total mass ratio and the last
  column includes the disc optical radius defined to be the radius at which the
  $B$-band surface brightness drops below 25 mag arcsec$^{-2}$ \citep{auriga}.
  The largest correlations are found for the two smaller radii and
  dilute as one approached $R_{200}$.
  Large and massive stellar discs with a low gas content are
  correlated with low dark matter triaxilities.}
\label{fig:disc_correlations}
\end{figure*}

\begin{figure*}
\begin{center}
\includegraphics[width=0.9\textwidth]{correlations_angles_alignment_MHD.pdf}
\end{center}
\caption{Changse of angle alignment of the dark
  matter halo and stellar disc at two different radii ($R_{200}/16$
  and $0.25R_{200}$) as a function of the baryonic disc properties
  already explored in Figure \ref{fig:disc_correlations}.  
  Figure \ref{fig:cumulative_alignment} showed that maximum alignment
  occurs at $0.25R_{200}$ while in the inner regions ($R_{200}/16$)
  considerable missalignments occurr.
 at different radii
 and baryonic disc properties. 
 The label with the $\rho$ value corresponds to the Spearman’s rank correlation coefficient. }
\label{fig:alignment_correlations}
\end{figure*}

@@

The left panel of this Figure shows that in the DMO sample the
triaxility has a median larger than $0.5$ at all radii, furthermore
this median value increases as we move towards the inner part of the
halo.
The right panel shows the exact complementary picture in the MHD
sampe.
There the median triaxility is alwas smaller than $0.5$ and this
triaxility is smaller as we move closer to the galactic disc.

@@

\subsection{Alignments with the stellar disc}

A common assumption in observational models of the MW DM halo is that
its minor axis is perfectly aligned with the stellar disc minor axis.
Although it is a reasonable assumption to guarantee the stability of
the galactic disc in simplified models of isolated galaxies, this
might not hold in an explicit cosmological context. 
To examine the degree of validity of this assumption we study in this
section the alignment between the eigenvectors of the inertia tensor of
stellar particles within $0.1R_{200}$ ($\sim 23\pm 2$ kpc) and the
eigenvectors of the dark matter halo shape.
All the measurements are done at $z=0$.

In Figure \ref{fig:cumulative_alignment} we summarize our main results
regarding these alignments with the halo shape measured at five
different radii.
The upper row shows the alignment of the halos in the DMO simulations
with the stellar disc in the MHD simulations.
The main objective of this measurement is to calibrate the radial
evolution of the DM halo shape. 
We find that the DM shape remains constant with radius.

The lower row in Figure \ref{fig:cumulative_alignment} shows the
alignments with the halo in the MHD simulations. 
This time the halo shape changes and twists at different radii.
However around the radius of $0.25R_{200}$ there is an alignment
almost perfect between the shapes of the stellar disc and the dark
matter halo. 
Above and below this radius there are halos with a lower degree of
alignment.
Across the three different alignments we measure we verify that the
strongest one is indeed the one between the two minor axis.

@@

The strength of the change depends on the numerical resolution, the
method to resolve the hydrodynamics and the models describing star
formation and stellar feedback \citep{Debattista08, Bryan13, Butsky16,
  Chua19, Artale19}.  
The key concept unifying these results is that the baryon distribution
influences and correlates with the dark matter halo shape. 
Here we find that the broad tendency is that massive stellar discs
correlate with spherical dark matter distributions.

In order to explore this idea in the Auriga simulations we quantify
the correlation between halo shape with baryonic disc properties. 
Looking into the measurements already reported by \cite{auriga} and
\cite{Pakmor17} we find three baryonic quantities that have the
strongest correlation with DM halo triaxiality: the central gas
density in a sphere of radius $1$kpc, the disc to total mass ratio and
the optical radius.

Figure \ref{fig:disc_correlations} shows the correlations of
these quantities with the triaxility at five diferent radii.
We use the Spearmen's rank correlation coefficient to quantify the
correlation strength.
We find that the strongest correlations are found with the halo shape
measured at radii smaller than $0.12R_{200}\sim 28$kpc, which 
is close to the upper limit of the disc optical radius among our
simulation sample. 
The trend is such that halos with large triaxiality correlate with
high gas density and stellar discs with low mass and small size.
In turn, massive and large stellar discs within a low density gas
environment correlate with low halo triaxiliaty.

Our second results deals with the disc-halo shape alignment as a function of
radius. 
In concordance with previous results in DM only simulations we find
that the shells of halo shape are well aligned at different radii.
However, in the presences of baryons these shells twist as a function
of radius.
At a radius of $0.25R_{200}\approx 56$ kpc the alignment between the
stellar disc and the dark matter halo is almost perfect and degrades
at other radii. 
This twisting effect, the change of disc-halo alignment as
a function of radius, is robust across our sample of 30
halos at all radii.
However, its strenght is not the same for all galaxies and strongly
correlates with halo triaxiality measured at $0.12R_{200}$.

\cite{Bailin05} studied the disc halo alignmnent as a function of
radius.
\cite{Gomez17} studied this in Auriga.
\cite{Debattista13} reported a similar twisting effect, but only at radii smaller
than the disc radius. 
At radii larger than the disc radius, they find, the dark matter
shells stop twisting. 
\cite{JingSuto02} also reported shell alignment twisting in their dark
matter only simulations as measured in the direction changes of large
and medium shape axis. 
They only had three high resolution MW-like halos (with
$\sim 10^{6}$ inside the virial radius) and could not make a
statistical statement about the impact of this effect.
However, they the twisting as an artifact resulting from high values of the
$c/b$ ratios that make the determination of the medium axis boisy.
Could then high triaxility values explain the twisting as a result of
erratic axis directions? 
If the triaxiality were the main culprit behind the twisting, the
correlation between the two quantities should be constant at every
radii.
In Figure \ref{fig:alignment_correlations} we already showed that this
correlation strongly depends on radius, we conclude that high
triaxiality values cannot be the full explanation.
Furthermore the twisting happens in such a way that it allows an
almost perfect alignment between the stellar disc at $0.1R{200}$ and
the halo shape measured at $0.25R_{200}$

We now use the results reported by \cite{LM10} and \cite{Bovy16}
to place our results in an observational context.
\cite{LM10} used observations of the Sagittarius tidal stream to
constrain the shape of the gravitational potential.
Their point of depart is that previous studies that assumed an
axisymetric galactic potential were not able to fit all the available
dynamic constraints for the Sagittarius stream, therefore making
necessary the use of a rigid triaxial potential with coaxial potential
ellipsoids for the dark matter component.  
Their results constrain the triaxility of this potential
component. 
They also translate ther results into a triaxiality of the density
contours (that could be compared against our results)
 to be $(c/a)=0.44$ and $(b/a)=0.97$ at a radius of $\sim 40$kpc. 
They do not report any uncertainties for these two values. 
Looking at their plots for the quality of fit criterion as a function
of dark halo axial scales (their Figure 5), we choose a conservative $10\%$
relative uncertainty.
One surprising element in their results is that  the major axis of the
halo shape is perpendicular to the stellar disc plane.

@@

In this paper we measured the shape of 30 isolated Milky Way like 
dark matter haloes simulated in the Auriga project using the zoom-in
technique. 
The Auriga project simulated these halos with two different setups:
dark matter only (DMO) simulation and full magnetohydrodynamics (MHD)
including star formation and feedback.
We used the shape measurement algorithm by \cite{Allgood06} on the
dark matter halos of these two kinds of simulations to quantify the
halo shape as a function of radius and the degree of aligment between
the stellar disc and the halo.

We find that MHD halos are rounder than DMO halos at every radius.
MHD halos tend towards more oblate shapes ($T<1/3$), while DMO halos
tend towards more prolate shapes ($T>2/3$).  
The rounding effect is more noticeable as one moves closer to galactic
disc and strongly  correlates with baryonic properties of the disc
More precisely, the triaxility is smaller for large and massive
stellar discs with low gas densities at its core.

We also measured the shape alignment of the halo with the stellar
disc.
At a radius of $0.25R_{200}$ the alignment is almost perfect and
degrades at smaller and larger distances.
We found that in some halos the alignment betwen the stellar disc
and dark matter halo changes noticeably with the radius.
This alignment evolution implies a radial twisting between the ellipsoids
describing the halo shape. 
We quantify this twist with the standard deviation of the angle
between the two minor axis at radii below $\leq 0.5R_{200}$ and find
that it strongly correlates with the disc size and the core gas
mass density, there is only a weak correlation with the disc to
total mass ratio in the disc.

@@

From the purely numerical point of view a better understading of the
disc-halo alignment details will certainly require to study how the
halo and the disc co-evolved as a function of time.
Calibrating the effect of the cosmic web (both dark matter and gaseous)
\citep{2014MNRAS.443.1090F,2017MNRAS.469..594B,2019MNRAS.487.1607G}
could also be required to gain a full picture of this behaviour.
